Submodular Optimization for Control of Prosumer Networks

### 2016-04-21 Article.tex
monique corrections

We propose here an optimization method for the placement of storage in networks of prosumers that may both consume and produce electricity using renewable generators (DER). In this stochastic context, power imbalances are very likely, such that the system might lose synchrony and require control to bring it back to the synchronized state. We consider the control inputs as being the amount of power injected in the grid at the chosed storage locations. In a context where generators and loads are stochastic and not fixed, the optimal placement of the storages beforehand is not trivial. We model the dynamic as a system of differential equations and the physical constraints of the system are included. We then propose and validate an algorithm based on a submodular optimization that minimizes the average energy required to control the system.

@@

\section{Conclusion}
\label{sec:Conclusion}
In this paper, we considered the case of networks of prosumers which can behave as generators or loads depending on weather conditions. We proposed an optimization method of the storage placement in such a stochastic context through the optimal control theory. This approach enabled us to take the grid's dynamic and its physical constraints into account. Because perturbations could be of any kind and thus the control in an direction of the state space, our optimization method relies on submodular set functions and the gramian matrix, for minimizing the average energy that should be injected or absorbed by the storage equipments.

We believe that interesting work could be done by combining this model with real production and consumption data. There are indeed complex spatial and temporal correlations that impacts these distributions \cite{Gensollen2014}. In contrast, we considered that the control has to be in average in any direction of the state space but confronting this assumption with real traces could lead to interesting further research.

>>>>

We propose here an optimization method for the placement of storage in networks of prosumers that may both consume and produce electricity using renewable generators (DER). In this stochastic context, power imbalances are very likely, such that the system might lose synchrony and require control to bring it back to the synchronized state. We consider the control inputs as being the amount of power injected in the grid at the chosen storage locations. In a context where generators and loads are stochastic and not fixed, the optimal placement of the storages beforehand is not trivial. We model the dynamic as a system of differential equations and the physical constraints of the system are included. We then propose and validate an algorithm based on a submodular optimization that minimizes the average energy required to control the system.

@@

\section{Conclusion}
\label{sec:Conclusion}
In this paper, we considered the case of networks of prosumers which can behave as generators or loads depending on weather conditions. We proposed an optimization method of the storage placement in such a stochastic context through the optimal control theory. This approach enabled us to take the grid's dynamic and its physical constraints into account. Because perturbations could be of any kind and thus the control in any direction of the state space, our optimization method relies on submodular set functions and the gramian matrix, for minimizing the average energy that should be injected or absorbed by the storage equipments.

We believe that interesting work could be done by combining this model with real production and consumption data. There are indeed complex spatial and temporal correlations that impact these distributions \cite{Gensollen2014}. In contrast, we considered that the control has to be in average in any direction of the state space but confronting this assumption with real traces could lead to interesting further research.
